Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-15 WRITEUP/ms.tex
few modification to Sec. 5

The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold,  we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following. We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We note that the distributions vary for different evolutionary stages of \flower.
%
The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist}) corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
%
Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}). The main disk occupying the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
 over all times analyzed here.
Note that the scales shown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$.
\label{fig:dist}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
Definition of symbols are same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
post-starburst phase.
The variation is clearly seen between the pre-starburst through post-starburst phase.
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
\label{fig:alphaEvol}}
\end{figure*}

@@

We first present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$)
and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies,
such as the nearby gas-rich galaxy M64 and
% Kennicutt, 1996IAUS..171...11K
% Spiral gal, appears to have accreted a gas-rich companion in the recent past,
% with the inner gas disk the remnant of the
% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995).
the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are
composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component
(i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of
some of them (see \Fig{stellarRatio16}).
MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of
\Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower.
This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

@@

% Starburst
Focusing on MCCs in the starburst phase, they have similar velocity dispersion and sizes
as those in the accreting phase; however, the MCCs in the starburst phase span
a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters (thus, more susceptible to collapse).
Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
(\Fig{alphaEvol}).
Most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
This is consistent with our physical intuition of gas instability leading to \SF.

\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}

@@

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
For instance, the cluster of points found at the lowest density threshold,
occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28},
are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel.
In this way, we identify a population of denser molecular structures (see \Fig{MCC}).

We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been
reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
However, the IGM and merger and accretion histories are not properly modeled in such simulations since
they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
%%
%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%%
%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%%
This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.

@@

% temporal evolution in Cloud Dynamics
We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}.
We find no quantitative differences over the 700\,Myr traced in our simulation, except
for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).

>>>>

We start by considering the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the results for the distributions considering all the evolutionary stages and dividing the sample in a low ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
%
Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower.
%
The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
Definition of symbols are same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
post-starburst phase.
The variation is clearly seen between the pre-starburst through post-starburst phase.
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant} 
\label{fig:alphaEvol}}
\end{figure*}

@@

We can now focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}). Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.

During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
%
MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.

@@

% Starburst
In the starburst phase, MCC have similar velocity dispersion and sizes as those in the accreting phase; however, the MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters, i.e. they more susceptible to collapse. Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase 
%
\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
This is consistent with our physical intuition of gas instability leading to \SF.

\subsection{Adopted Density Threshold Dependence and Temporal Evolution}\label{sec:ncut}

@@

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
%
The cluster of points found at the lowest density threshold, occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
%
These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. In this way, we identify a population of denser molecular structures (see \Fig{MCC}).

We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
%
However, the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
%
The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
%%
%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
%%
%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
%%
This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.

@@

% temporal evolution in Cloud Dynamics
\AP{the following is cutting the discussion a bit too abruptly; additionally, it might seem contradicting with the fact that we find differences when analysing extreme stages}
We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. We find no quantitative differences over the 700\,Myr traced in our simulation, except for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
